Modelling BCG vaccination in the UK

### 2019-08-01 rmds/00-contribution.Rmd
reorganised thesis to work with online gitbook
Former-commit-id: 3fd8c59438bc22ef6b09d75159886a79ea855f4e
updated contribution
contribution updated

Abbott S, Christensen H, Lalor MK, Zenner D,Campbell C, Ramsay M, Brooks-Pollock E. *Exploring the effects of BCG vaccination in patients diagnosed with tuberculosis: observational study using the Enhanced Tuberculosis Surveillance system*, doi: https://doi.org/10.1101/366476 \par

>>>>

Abbott S, Christensen H, Brooks-Pollock E. *Reassessing the evidence for universal school-age Bacillus Calmette Guerin (BCG) vaccination in England and Wales*, doi: https://doi.org/10.1101/567511 \par

Abbott, S., Christensen, H., Lalor, M. K., Zenner, D., Campbell, C., Ramsay, M. E., & Brooks-Pollock, E. (2019). *Exploring the effects of BCG vaccination in patients diagnosed with tuberculosis: Observational study using the Enhanced Tuberculosis Surveillance system*. Vaccine, 1–6. doi: http://doi.org/10.1016/j.vaccine.2019.06.056 (preprint: https://doi.org/10.1101/366476) \par
